%The algorithm is presented below:-

%%%%%%%%%%%%%%%% alg-custom-block %%%%%%%%%%%%
\algblock{ArmElim}{EndArmElim}
\algnewcommand\algorithmicArmElim{\textbf{\em Arm Elimination by Mean Estimation}}
 \algnewcommand\algorithmicendArmElim{}
\algrenewtext{ArmElim}[1]{\algorithmicArmElim\ #1}
\algrenewtext{EndArmElim}{\algorithmicendArmElim}
\algtext*{EndArmElim}

\algblock{ArmElimV}{EndArmElimV}
\algnewcommand\algorithmicArmElimV{\textbf{\em Arm Elimination by Mean and Variance Estimation}}
 \algnewcommand\algorithmicendArmElimV{}
\algrenewtext{ArmElimV}[1]{\algorithmicArmElimV\ #1}
\algrenewtext{EndArmElimV}{\algorithmicendArmElimV}
\algtext*{EndArmElimV}

\algblock{ResetParam}{EndResetParam}
\algnewcommand\algorithmicResetParam{\textbf{\em Reset Parameters}}
 \algnewcommand\algorithmicendResetParam{}
\algrenewtext{ResetParam}[1]{\algorithmicResetParam\ #1}
\algrenewtext{EndResetParam}{\algorithmicendResetParam}
\algtext*{EndResetParam}

\begin{algorithm}[th!]
\caption{AugmentedUCB}
\label{alg:augucb}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, exploration parameters $\rho$, $\rho_v$ and $\psi$, threshold $\tau$.
\State {\bf Initialization:} Set $B_{0}:=A$, $M=\bigg\lfloor \dfrac{1}{2}\log_{2} \dfrac{T}{e}\bigg\rfloor $, $m:=0$, $\epsilon_{0}:=1$, $\ell_{0}=\big\lceil \dfrac{2\log(\psi T\epsilon_{0}^{2})}{\epsilon_{0}} \big\rceil$ and $N_{0}=K*\ell_{0} $.
\State Pull each arm once
%\State \For{$m=0,1,..\big \lfloor \dfrac{1}{2}\log_{2} \dfrac{T}{e}\big\rfloor$}{	
%\State $N_{0}=\big\lfloor \dfrac{T}{M} \big\rfloor$
\State \For{$t=K+1,..,T$}
%\State Pull arm $i$ in $B_m$ such that $\min_{i\in B_{m}}\bigg\lbrace |\hat{r}_{i} - \tau | - \sqrt{\dfrac{\rho_v \hat{V}_{i} \log (\psi T \epsilon_{m}^{2})}{4 n_{i}} + \dfrac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}} \bigg\rbrace$, where $n_{i}$ is the number of times the arm $i$ has been pulled.
\State Pull arm $i$ in $B_m$ such that $\min_{i\in B_{m}}\bigg\lbrace |\hat{r}_{i} - \tau | - s_{i}\bigg\rbrace$
\State $t:=t+1$ 
\ArmElim
\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
\begin{align*}
%\hat{r}_{i} + \sqrt{\dfrac{\rho\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}}  < \tau -\sqrt{\dfrac{\rho\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}} 
\hat{r}_{i} + c_i  < \tau - c_i
\end{align*}
\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
\begin{align*}
%\hat{r}_{i} - \sqrt{\dfrac{\rho\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}}  > \tau +\sqrt{\dfrac{\rho\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}} 
\hat{r}_{i} - c_i  > \tau + c_i
\end{align*}
where $ c_i=\sqrt{\frac{\rho\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}} $
\EndArmElim
\ArmElimV
\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
\begin{align*}
%\hat{r}_{i} + \sqrt{\dfrac{\rho_v\hat{V}_{i}\log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}} + \dfrac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}}  < \tau -\sqrt{\dfrac{\rho_v\hat{V}_{i}\log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}} + \dfrac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{2 n_{i}}} 
\hat{r}_{i} + s_i  < \tau - s_i 
\end{align*}
\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
\begin{align*}
%\hat{r}_{i} - \sqrt{\dfrac{\rho_v\hat{V}_{i}\log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}} + \dfrac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}}  > \tau +\sqrt{\dfrac{\rho_v\hat{V}_{i}\log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}} + \dfrac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}} 
\hat{r}_{i} - s_i  > \tau + s_i
\end{align*}
where $s_i=\sqrt{\frac{\rho_v\hat{V}_{i}\log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}} + \frac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}}$
\EndArmElimV
\State \If{$t\geq N_{m}$ and $m \leq M$}
\ResetParam
\State $\epsilon_{m+1}:=\dfrac{\epsilon_{m}}{2}$
\State $B_{m+1} := B_{m}$
%\State $p_{m+1}:=p_{m}+1$
%\State $M := \dfrac{p+1}{p}$
\State $\ell_{m+1}=\bigg\lceil \dfrac{2\log(\psi T\epsilon_{m+1}^{2})}{\epsilon_{m+1}} \bigg\rceil$
\State $N_{m+1} := t + |B_{m+1}|\ell_{m+1}$
% + \lfloorM N_{m}\rfloor $
\State $m := m+1$
\EndResetParam
\EndIf
\EndFor
\State Output $\hat{S}_{\tau}=\lbrace i: \hat{r}_{i}\geq \tau \rbrace$.
\end{algorithmic}
\end{algorithm}

In algorithm \ref{alg:augucb}, hence referred to as AugUCB, we have three exploration parameters, $\rho, \rho_v$ which are the arm elimination parameters and $\psi$ which is the exploration regulatory factor. The threshold $\tau$ is also given as an input. AugUCB combines the power of UCB-Improved (\cite{auer2010ucb}), APT (\cite{locatelli2016optimal}) and SAR (\cite{gabillon2011multi}) or CSAR(\cite{chen2014combinatorial}). The main approach is based on UCB-Improved with modifications suited for the thresholding bandit problem. The active set $B_{0}$ is initialized with all the arms from $A$. We divide the entire budget $T$ into rounds/phases as like UCB-Improved, SAR and CSAR. The choice of $M$ comes from UCB-Improved which necessarily entails that the $\epsilon_{m}\geq \sqrt{\frac{e}{T}}$. So, $M$ is the total number of rounds and is the same as UCB-Improved. After the end of each such round $m$ we eliminate arm(s) from active set $B_{m}$ and update parameters. 
	
	As suggested by \cite{liu2016modification} to make AugUCB an anytime algorithm and to overcome too much early exploration, we no longer pull all the arms equal number of times in each round but pull the arm that minimizes,  
\begin{align*}
\min_{i\in B_{m}}\bigg\lbrace |\hat{r}_{i} - \tau | - \sqrt{\frac{\rho_v \hat{V}_{i} \log (\psi T \epsilon_{m}^{2})}{4 n_{i}} + \frac{\rho_v \log{(\psi T\epsilon_{m}^{2})}}{4 n_{i}}} \bigg\rbrace
\end{align*}
in the active set $B_{m}$. This condition makes it possible to pull the arms closer to the threshold $\tau$ and with suitable choice of $\rho,\rho_v$ and $\psi$ we can fine tune the exploration. The exact choices for these parameters are derived in Corollary \ref{Result:Corollary:1}. This is a strategy used by APT. Also, unlike SAR or CSAR, we do not have explicit accept or reject set rather the arm elimination conditions simply removes arm(s) if the algorithm is sufficiently sure that the mean of the arms are very high or very low about the threshold based on mean or variance estimation. This although is a tactic similar to SAR or CSAR, but here at any round, an arbitrary number of arms can be accepted or rejected thereby improving upon SAR and CSAR which accepts/rejects one arm in every round. At the end of the budget $T$ the algorithm outputs all the arms whose estimated average payoff $\hat{r}_{i}$ is above the threshold $\tau$ thereby making this an anytime algorithm whereby we need not finish every round. The arm elimination conditions helps in re-allocating the remaining budget/pulls among the surviving arms.

%Also, like SAR or CSAR, we do not have explicit accept or reject set. Rather 
